Generalised gravitational burst generation with Generative Adversarial Networks

### 2020-07-03 Paper_draft/main.tex
changes to cGAN

\begin{figure}
    \centering
        \input{figures/GAN_diagram_vertical}%     without .tex extension
        \input{figures/ACGAN_diagram_vertical}%     without .tex extension
    \caption{Comparison of the original GAN method and the Auxiliary
Conditional-GAN method. For ACGANs the training data requires a label denoting
its class that is also fed to the generator which then learns to generate
waveforms based on the input label. Additionaly, the discrminator learns to
classify which class the signal belongs to. \jordan{change to cGAN}} \label{fig:gan_comparison}
\end{figure}

@@

All training waveforms are sampled at 1024 Hz.
%

\subsection{Applying a time shift and antenna responses}

% Explain the effect of the sky position 
%
We consider a two detector case~\chris{why 2 detector and not 3?} in which the
generator is trained to output two identical signals with a physical time shift
representing the time of flight between detectors H1 and L1 To achieve this, the generator
is trained to output a single waveform that is then put through a non-trainable
``response" layer before the output of the generator. This layer takes as input, the generated waveform, time delay and antenna responses. The sky location is chosen by drawing from a uniform distribution across the whole sky and the time delay, and antenna responses generated by LALSimulation~\cite{lalsuite}.

This response layer Fourier transforms the waveform
to the frequency domain, multiplies this by $e^{2 \pi i f \Delta t}$, where $\Delta
t$ is the time shift and transforming back
to the time domain. After which, both original and shifted signals are
multiplied by their respective  antenna responses. The output is two 1024 Hz times series waveform split into two channels.
This scheme is also used in generating the
training set.

@@

% specifically define our architecture
%
We adopt the suggestions of \cite{Radford2015,DBLP:journals/corr/abs-1809-11096}, lengthening
one-dimensional convolution kernels on both the generator and discriminator.
The Generator model is fully convolutional, upsampled using strided transposed
convolutions with batch normalisation in the first layer and ReLU activations
throughout with the exception of Tanh for the output layer. Each transposed
convolutional layer uses a kernel size of $18\times 1$ and stride of 2. The
discriminator network mirrors that of the generator without batch
normalization, using LeakyReLU activations, SpatialDropout, and a 2-stride
convolution for downsampling. The discriminator has two output layers: the
first output is a single node activated by a Sigmoid that can be interpreted as
the realness of the the signal, the second output is 5 nodes activated using
the softmax function predicting the class of the input.  This model is trained
with binary cross entropy for the first output and sparse categorical
cross-entropy for the second output. The full architecture description can be seen in \cref{Tab:hyperparameters}.~\chris{OK, very technically tight but too
computer sciencey. Try to make it human readbale for a physicist and refer to
the table of parameters in the appendix.}

@@

\subsection{Class labels and embedding}

% explain embedding
%
A learned embedding is an efficient way of representing categorical or class
based data. In contrast to traditional "one-hot encoding" where each class is
represented by a binary sparse vector, embeddings map each class to its own
distinct vector of a given size. The elements of these vectors are initialized
randomly and tuned during training just like weights~\chris{I thought that they
weren't trained. Are they definitely trained? Is this not just a single fully
connected layer that turns 5 numbers into 120? How is it any different to
that?}. ~\jordan{each class is one number that is turned into 120 numbers, embedding keeps track of the 5x120 numbers and as its training similar classes are grouped together in the class space. This explains it better than i can: https://machinelearningmastery.com/what-are-word-embeddings/ } This reduces computational cost as the sparse vectors containing mostly
zeros are not needed and allows related classes to cluster together. Once the
networks are trained the learned embedding vectors can be extracted from the
model and used as inputs to the generator. The benefit here is that the former
integer class labels are replaced by higher dimensional vector representations
allowing for finer experimenting in other applications. The class label is
interpreted as an additional channel early in the generator model. This is
achieved by projecting the class inputs as a learned embedding layer, into a
fully connected layer or "dense" layer which can then be concatenated
channel-wise to $\textbf{z}$.~\chris{very nice but still a bit too technical
without consideration for lowly astrophysicists. Can you soften it a bit to
make it more accessible. Explain more of the concepts when you introduce them.}

\chris{Also, it isn't clear where this comes into your analysis and why it's
important. I'm not sure that the definition of "signal class" has been made
anywhere.}

@@

>>>>

\begin{figure}
    \centering
        \input{figures/GAN_diagram_vertical}%     without .tex extension
        \input{figures/ACGAN_diagram_vertical}%     without .tex extension
    \caption{Comparison of the original GAN method and the
Conditional-GAN method. For CGANs the training data requires a label denoting
its class that is also fed to the generator which then learns to generate
waveforms based on the input label.} \label{fig:gan_comparison}
\end{figure}

@@

All training waveforms are sampled at 1024 Hz.

@@

% specifically define our architecture
%
We adopt the suggestions of \cite{Radford2015,DBLP:journals/corr/abs-1809-11096}, lengthening
one-dimensional convolution kernels on both the generator and discriminator.
The Generator model is fully convolutional, upsampled using strided transposed
convolutions with batch normalisation in the first layer and ReLU activations
throughout with the exception of Tanh for the output layer. Each transposed
convolutional layer uses a kernel size of $18\times 1$ and stride of 2. The
discriminator network mirrors that of the generator without batch
normalization, using LeakyReLU activations, SpatialDropout, and a 2-stride
convolution for downsampling. The discriminator output is a single node activated by a Sigmoid that can be interpreted as
a probability of the the signal being real. This model is trained
with binary cross entropy for the first output and sparse categorical
cross-entropy for the second output. The full architecture description can be seen in \cref{Tab:hyperparameters}.~\chris{OK, very technically tight but too
computer sciencey. Try to make it human readbale for a physicist and refer to
the table of parameters in the appendix.}

@@

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/sg_bbh_interp.pdf}
    \caption{Class space interpolation with latent space held constant throughout. The full 1s interval is plotted for class based interpolations between a Sine-Gaussian and a BBH in spiral.}
    \label{fig:sgbbh_interp}
\end{figure}
